Location and Scale-Invariant Power Transformations for Transforming Data to

### 2025-10-17 manuscript_rmarkdown/manuscript.Rmd
Insert sentence on presence of shift parameter in Box and Cox (1964).

Box-Cox and Yeo-Johnson transformations are modified by introducing
shift parameter $x_0$ and scale parameter $s$ into equations \ref{eqn:box-cox-original} and \ref{eqn:yeo-johnson-original}.
The location- and scale-invariant Box-Cox transformation of a feature value 
$x_i$ of feature $\mathbf{X}$ under transformation parameter $\lambda$, shift parameter $x_0$ and scale parameter $s$ 
is then defined as:

>>>>

@Box1964-mz originally included a shift parameter in their transformation, but
for their formal analysis set it to $0$, whereas @Yeo2000-vw did not include
a shift or scale parameter. Here, Box-Cox and Yeo-Johnson transformations are modified by introducing
shift parameter $x_0$ and scale parameter $s$ into equations \ref{eqn:box-cox-original} and \ref{eqn:yeo-johnson-original}.
The location- and scale-invariant Box-Cox transformation of a feature value 
$x_i$ of feature $\mathbf{X}$ under transformation parameter $\lambda$, shift parameter $x_0$ and scale parameter $s$ 
is then defined as:
